Placeholder

### 2021-02-06 Paper_Histograms.Rmd
Added chunk to get positive/negative psychosis diagnosis for GLAD/EDGI prepan

@@

>>>>

```{r Get OCDs positive for GLAD/EDGI}

@@

```{r Get psychosis positive for GLAD/EDGI}

GLAD.prepan_psychosis_positive <- GLAD.prepan %>%
  select(psychotic_disorders_numeric) %>% 
  filter(psychotic_disorders_numeric == 1)

GLAD.prepan_psychosis_positive <- GLAD.prepan_psychosis_positive %>% 
  summarise("Psychotic disorders" = n())
